Pyrovelocity Notebook Usage Example

### 2024-03-26 nbs/templates/user_example/user_example.qmd
chore(nbs): `530-nbwf` -> `beta` Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

def setup_pyrovelocity():
    if is_module_available("pyrovelocity"):
        try:
            import pyrovelocity
        except (ImportError, AssertionError):
            print("pyrovelocity is not successfully installed")
            sys.exit()
    else:
        print("Installing pyrovelocity...")
        install_package("pyrovelocity[workflows] @ git+https://github.com/pinellolab/pyrovelocity.git@530-nbwf")
        try:
            import pyrovelocity

>>>>

def setup_pyrovelocity():
    if is_module_available("pyrovelocity"):
        try:
            import pyrovelocity
        except (ImportError, AssertionError):
            print("pyrovelocity is not successfully installed")
            sys.exit()
    else:
        print("Installing pyrovelocity...")
        install_package("pyrovelocity[workflows] @ git+https://github.com/pinellolab/pyrovelocity.git@beta")
        try:
            import pyrovelocity

### 2024-03-26 scripts/examples/pypi_template/pyrovelocity_pypi_user_template.qmd
chore(nbs): `530-nbwf` -> `beta` Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

<a target="_blank" href="https://colab.research.google.com/github/pinellolab/pyrovelocity/blob/530-nbwf/docs/source/notebooks/pyrovelocity_pypi_user_template.ipynb">
  <img 
    src="https://colab.research.google.com/assets/colab-badge.svg" 
    alt="Open In Colab"
    width="109" height="20"/>
</a> <a target="_blank" href="https://nbviewer.jupyter.org/github/pinellolab/pyrovelocity/blob/530-nbwf/docs/source/notebooks/pyrovelocity_pypi_user_template.ipynb">
  <img 
    src="https://raw.githubusercontent.com/jupyter/design/master/logos/Badges/nbviewer_badge.png"
    alt="Render with nbviewer" 
    width="109" height="20"/>
</a>

>>>>

<a target="_blank" href="https://colab.research.google.com/github/pinellolab/pyrovelocity/blob/beta/docs/source/notebooks/pyrovelocity_pypi_user_template.ipynb">
  <img 
    src="https://colab.research.google.com/assets/colab-badge.svg" 
    alt="Open In Colab"
    width="109" height="20"/>
</a> <a target="_blank" href="https://nbviewer.jupyter.org/github/pinellolab/pyrovelocity/blob/beta/docs/source/notebooks/pyrovelocity_pypi_user_template.ipynb">
  <img 
    src="https://raw.githubusercontent.com/jupyter/design/master/logos/Badges/nbviewer_badge.png"
    alt="Render with nbviewer" 
    width="109" height="20"/>
</a>
